Synthesizing Quotient Lenses

### 2018-03-13 papers/QuotientLenses/main.tex
extended caption on ast graph
fixed caption in performance graph

\begin{figure}[t]
\includegraphics{generated-graphs/asts.eps}
\caption{AST node measurements for each of the three approaches
on each of the 10 non-bijective benchmark problems.
QRE Synthesis requires far fewer AST nodes than the other
two approaches.}
%%\caption{Count of benchmark programs definable using a given AST count. We find
%%that it takes far fewer AST nodes to define benchmark lenses using QRE
%%synthesis than with Optician without QRE synthesis or without synthesis.}
\label{fig:asts}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run the
  original version of Optician (\OpticianRuntime{}) and \QOpt{}
  (\QREOptician{}) on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  (In other words, we restored them to their original state with QREs
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics{generated-graphs/asts.eps}
\caption{AST node measurements for each of the three approaches
on each of the 10 non-bijective benchmark problems.
Benchmarks are sorted in order of increasing complexity as measured by
the number of AST nodes in the source and target format descriptions. 
QRE Synthesis requires far fewer AST nodes than the other
two approaches.}
%%\caption{Count of benchmark programs definable using a given AST count. We find
%%that it takes far fewer AST nodes to define benchmark lenses using QRE
%%synthesis than with Optician without QRE synthesis or without synthesis.}
\label{fig:asts}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run the
  original version of Optician (\OpticianRuntime{}) and \QOpt{}
  (\QREOptician{}) on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  and then extending the synthesis specification to include QREs.
  (In other words, we restored them to their original state, added QREs,
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}
